Which Scenario Should We Design For? Insights from House Elevation on the Multiple PDF Problem

### 2021-10-13 papers/operationalizing-bayesian-checking.tex
add some notes highlighting Klaus's comments

% page size and margins
\usepackage{geometry}
\geometry{letterpaper,margin=1in}

@@

@@

\begin{abstract}
    Many homeowners in the coastal zone elevate their houses to manage flood risk.
    Federal guidance for this decision relies on floodplain maps that are silent on projected future changes and neglect the deep and dynamic uncertainties surrounding the projected hazards.
    This uncertainty poses challenges for the design of decision-support systems.

@@

\subsection*{Submission Plan}
We should revisit this!
\begin{enumerate}
    \item Earth's Future
    \item Climatic Change
    \item IOP Environmental Research: Infrastructure and Sustainability (new journal)
    \item Risk analysis
\end{enumerate}
\subsection*{Internal peer review}
\begin{enumerate}
    \item TBD
\end{enumerate}

@@

\paragraph{Why this problem is important}
Since infrastructure built today is likely to persist for several decades, infrastructure designs must take into account the stresses that a project is likely to face far into the future.
On the one hand, overly optimistic assumptions of future risk can lead to unacceptably high risk of failure in the future if additional investments are not made.
For example, a failure to prepare Texas's interconnected natural gas, electricity, and water systems for temperatures that had been observed in the past 30 years caused cascading failures with disparate impacts \citep{doss-gollin_txtreme:2021}.
On the other, unless opportunity costs are negligible, designing for a too-pessimistic scenario can contribute to maladptation by limiting resource availability in the future.
For example, (\texttt{megaproject example})\ldots.

\paragraph{Present the Multiple PDF Problem}
While classical utility- or regret-based frameworks offer a structure for weighing these risks, they are not designed to handle uncertainties that are \emph{deep} in the sense that stakeholders may not agree upon their probabilities \citep{lempert_complex:2002} or \emph{irreducible} in the sense that there is not an objective truth that better models and data can identify \citep{DossGollin:2019}.\footnote{Unless we believe everything is pre-determined, in which case why bother with climate adaptation\ldots}
Examples of such uncertainties include how much greenhouse gasses humans will emit in the future or whether the U.S. federal government will continue to subsidize flood insurance for homeowners.
In response, a wide range of fields have developed scenario-based methods\ldots.
This leads to the ``Multiple PDF Problem'' \citep{sharma_rcp:2021}\ldots.
A key question, then, facing the designers, builders, regulators, owners, and users of built facilities is \emph{to which scenario should infrastructure be designed?}

\paragraph{Set up house elevation as an example}
One example is building codes and guidelines\ldots.
Prior studies have found that floodproofing and building-scale vulnerability reduction measures, including house elevation, can effectively reduce local flood damages in many contexts \citep{demoel_reducing:2014,deruig_building:2020,kreibich_building:2005,slotter_floodproofing:2020,Rozer:2016dn,mobley_mitigation:2020,aerts_cost:2018}.
Official guidance for homeowners, notably from \gls{fema}, recommends elevating to the \gls{bfe} (typically the \SI{100}{year} flood) plus a freeboard \citep{fema_retrofitting:2014,asce_24-14:2015,fema_retrofitting:2014} but recent suggests scope for improvement.
For example, \citet{xian_elevation:2017} used a cost-benefit analysis to demonstrate that tailoring recommendations to the inital elevation of a structure can reduce expected costs.
\citet{zarekarizi_suboptimal:2020} showed that neglecting uncertainty in discount rate, house lifespan, flood risk, and depth-damage curves can lead to maladaptation.
Yet these studies are silent on the question of how nonstationary flood hazard should factor into this decision.

\paragraph{Nonstationarity motivates the case study}
Nonstationarity is particularly relevant in coastal communities where \gls{rslr} is expected to drive future flood risk.
As a didactic case study, we consider the problem of how high a homeowner should elevate their structure to mitigate future flood losses, illustrated in \cref{fig:house-sketch}, given stochastic flood peaks and deeply uncertain \gls{rslr}.
\Gls{rslr} is driven mainly by physical processes like (\ldots, West Antarctic Ice Sheet, \ldots) \citep{kopp_probabilistic:2014,kopp_evolving:2017}.
Two key uncertainties identified by previous studies are
\begin{enumerate*}[label=(\roman*)]
    \item which emissions pathway (\eg, \gls{rcp} scenario) will we experience and
    \item how will polar ice sheets respond to warming \citep{wong_brick0.2:2017,ruckert_coastal:2019,wong_nola:2017,deconto_antarctica:2016}.
\end{enumerate*}
Simulations of \gls{rslr} are available to decision makers grouped by \gls{rcp} scenario and model structure.
For a given combination of \gls{rcp} scenario and model, results are typically presented and interpreted as probabilistic, but this is not the same as giving decision-makers a single \gls{pdf}.
This is the ``Multiple \gls{pdf} Problem'' described in, \eg, \citet{sharma_rcp:2021}.
Thus, \emph{which scenario/\gls{pdf} should we design for?}

@@

\begin{figure}
    \centering
    \includegraphics[height=2in]{uconn-elevateA}
    \caption{
        Conceptual sketch illustrating the path from historical data to FEMA's guidance.
        This figure SHOULD BE MODIFIED to have three panels, of which this is the third.
        (a): A time series of historical floods.
        (b): A \gls{pdf} of the flood peak.
        (c): as shown, but with waves eliminated.
        This sketch figure is from \citet{patten_elevate:2016}.
    }\label{fig:house-sketch}
\end{figure}

@@

In this section we present a general framework for decision making under deep uncertainty.
We begin with terms and definitions that are broadly consistent with the rest of the literature.
In \cref{sec:methods-weight} we present a Bayesian model for weighting \glspl{sow}.
In \cref{sec:methods-iterative} we discuss how this framework can be integrated into frameworks for iterative engagement with experts and stakeholders to expand and frame the model.

@@

We start by modeling the performance of a given decision $x \in \mathcal{X}$.
To do this, we will use a system model $f: \mathcal{X}, \Omega \rightarrow \mathcal{U}$ which takes as inputs the decision $x_i$ and a state of the world $s$ and returns one or more metrics of interest, $u$ \citep[we generally follow the notation of][]{mcphail_robustness:2019}.
We assume $f$ to be deterministic; if $f$ is a stochastic function we can use a technique like Monte Carlo sampling to estimate expectated values of the metrics, \ie $u_{ij} = \mathbb{E}\qty[u | x=x_i, s=s_j]$ (in the limit where the expectation can be calculated exactly, $f$ behaves like a deterministic function).

@@

\citet{mcphail_robustness:2019} split the problem of aggregating \gls{sow} metrics into decision metrics into two steps: ``subsetting'' (\eg, single value, all values, subset of values) and ``metric calculation'' (\eg, mean, variance, skew, kurtosis).
We generalize this to
\begin{equation}
    m_i = g(\qty{u_{i1}, u_{i2}, \ldots, u_{iJ}}, \qty{w_1, w_2, \ldots, w_J}),
\end{equation}
where $g$ is an \emph{aggregating function} describing the ``metric calculation'' step and the $w_j$ describe weights given to each \gls{sow}.
A optional, but likely useful, interpretation of the weighted samples $\qty{w_j, u_{ij} \forall j=1, \ldots, J}$ is an empirical \gls{pdf}, in which case $g$ maps a \gls{pdf} of future outcomes to the metrics $m_i$.\footnote{perhaps this belongs in the Discussion}
This is a flexible framework; \cref{tab:literature-weighting} shows some methods for robust decision making from the literature using our notation.

@@

\paragraph{To think  about}
I have two flavors of this idea presented here!
\Cref{fig:framework} takes a more Bayesian focus: the goal is to reason about properties of the \emph{distribution} over outcomes $p(u | x=x_i)$.
The text follows \citet{mcphail_robustness:2019} more.
I'm not sure which is easier to understand.

@@

Settinget all $w_j \propto 1$ as is often done (\cref{tab:literature-weighting}) reveals a tension: we want to \emph{explore} highly unlikely but theoretically possible trajectories to understand their consequences, but we don't want extremely unlikely scenarios to dominate our decision.

Some aims:
\begin{enumerate}
    \item We should be invariant to the parameterization of $s$ -- if we sample population uniformly from 1 million to 10 million or $\log_{10}$ population uniformly from \num6 to 7, we should get the same answer
    \item We should be invariant to the sampling of $s$:
          \begin{enumerate}
              \item if we include scientifically interesting but extremely low-probability scenarios (\eg, if someone created \gls{rcp} 45), our esimtates of $m_i$ should not change meaningfully
              \item if we include nearly redundant scenarios (\eg, if we are studying \gls{rcp} 2.6, 4.5, 6.0, and 8.5 and we then add results from a \gls{rcp} 6.01 experiment), our estimates of $m_i$ should not change meaningfully
          \end{enumerate}
    \item Our assumptions should be transparent and open to critique
\end{enumerate}
We can do this with probability if we have a target distribution $p(s)$.
We return to the question of how to choose this in \cref{sec:methods-prior}.

@@

\begin{figure}
    \centering
    \includegraphics[height=2.5in, width=0.6\textwidth, keepaspectratio=true]{xlrm}
    \caption{
        XLRM diagram.
        Red nodes represent uncertainties ($X$).
        Yellow node represents the lever ($L$).
        The gray node shows system relationships ($R$).
        Blue nodes show metrics ($M$).
    }\label{fig:xlrm}
\end{figure}

@@

Coastal floods are often decomposed into changes in local sea level \citep{kopp_evolving:2017,kopp_probabilistic:2014,wong_brick0.2:2017} plus storm surge \citep{garner_slrise:2018,cagigal_emulator:2020,rueda_surge:2016}.
We neglect waves and hydrodynamics because (FILL IN)\ldots.

\gls{rslr}:
\begin{enumerate}
    \item We have 2 models of ice sheet dynamics (3? Vivek and Tony are trying to tell me what models the data from \citet{ruckert_coastal:2019} actually comes from)
    \item We have 4 \gls{rcp} scenario
    \item We use the BRICK \citep{wong_brick0.2:2017} simulations from \citet{ruckert_coastal:2019} to define $J$ \glspl{sow}.
\end{enumerate}
Storm surge:
\begin{enumerate}
    \item We have a $N$ year observational record
    \item We separate out storm surge from the background trend in some standard way
    \item We model storm surge as a stationary GEV model
    \item We apply clever priors: we place a prior on the return level (data space) rather than a prior on the parameters themselves (except the shape parameter -- we put a restrictive prior for it to be positive)\footnote{arguably we should stick to boring priors here -- the question being whether it's better to say we use iterative checks to improve the priors, or whether we want to keep things simple}
    \item We draw $K$ sets of parameters $\qty(\mu_k, \sigma_k, \xi_k)$
\end{enumerate}
Thus a \gls{sow} is defined just an 81 year time series of \gls{lsl}.
We will see what we do with the $K$ draws of storm surge parameters shortly.
\begin{figure}
    \caption{
        INSERT HERE: figure showing time series of observed surge and \gls{lsl} with notable storms indicated, as well as projections of future \gls{lsl} under all eight models (two BRICK, four \gls{rcp})
    }
\end{figure}

@@

\subsection{System model}

@@

\paragraph{Prior on outputs only}
Following \citet{garner_slrise:2018}, \citet{oddo_coastal:2017}, and \citet{lempert_slr:2012} we place a prior on \gls{rslr} in 2100.

@@

                    More recent discussions of Bayesian philosophy \citep{jaynes_probability:2003,McElreath:2016vu,Gelman:2014tc,bernardo_bayesian:1994} also emphasize a philosophical view of probability as a language with which to reason about the unknown rather than a statement of objective truth \citep[see][for a thorough discussion of Bayesian philosophy]{gelman_philosophy:2013}.

@@

              \item A goal is to make -- intrinsically flawed and subjective -- modeling choices as transparent as possible. Since we can't be right, we should make it as easy as possible for others to understand and critique our assumptions

@@

\begin{enumerate}
    \item MARISA (details!) for JDG funding
    \item PSIRC (details!) for JDG funding
    \item Rice University (do I need to thank startup?)
    \item Tor Erlend Fjelde for helpful advice on implementing the GEV prior using \texttt{Turing.jl}.
\end{enumerate}

>>>>

% page size and margins
\usepackage{geometry}
\geometry{letterpaper,top=1in, bottom=1in, left=0.5in, right=2in}

@@

% TO DO NOTES
\usepackage{xcolor} % list of colors at https://en.wikibooks.org/wiki/LaTeX/Colors
\definecolor{giallo}{HTML}{F0BC42} % https://teamcolorcodes.com/a-s-roma-color-codes/
\definecolor{rosso}{HTML}{8E1F2F}
\definecolor{grigio}{HTML}{CACACC}
\definecolor{nero}{HTML}{000000}
\usepackage[textsize=scriptsize]{todonotes}
\setlength{\marginparwidth}{1.75in}
\newcommand{\james}[1]{\todo[color=giallo, textcolor=nero]{\textbf{ATTN James:~}#1}} % if desired create a custom command for each author
\newcommand{\klaus}[1]{\todo[color=rosso, textcolor=grigio]{\textbf{ATTN Klaus:~}#1}}

@@

\begin{abstract}
    Many homeowners in the coastal zone elevate their houses to manage flood risk.
    Federal guidance for this decision relies on floodplain maps that are silent on projected future changes and neglect the deep and dynamic uncertainties surrounding the projected hazards.
    This uncertainty poses challenges for the design of decision-support systems.\james{If this is about RDM then let's lead with that.}

@@

\section*{Front Matter}

\subsection*{Submission Plan}
We should revisit this!
\begin{enumerate}
    \item Earth's Future
    \item Climatic Change
    \item IOP Environmental Research: Infrastructure and Sustainability (new journal)
    \item Risk analysis
\end{enumerate}
\subsection*{Internal peer review}
\begin{enumerate}
    \item Vivek
    \item Courtney
    \item Sanjib
    \item Kelsey to replicate code
\end{enumerate}

@@

\paragraph{Why this problem is important}
Since infrastructure built today is likely to persist for several decades, infrastructure designs must take into account the stresses that a project is likely to face far into the future.
On the one hand, overly optimistic assumptions of future risk can lead to unacceptably high risk of failure in the future if additional investments are not made.
For example, a failure to prepare Texas's interconnected natural gas, electricity, and water systems for temperatures that had been observed in the past 30 years caused cascading failures with disparate impacts \citep{doss-gollin_txtreme:2021,busby_cascadingrisks:2021}.
On the other, unless opportunity costs are negligible, designing for a too-pessimistic scenario can contribute to maladptation by limiting resource availability in the future.
For example, \ldots\james{add an example of a maladaptive megaproject -- look to sustainability science or the arguments in \citet{ansar_bigisfragile:2017}.}

\paragraph{Set up the ``Multiple PDF Problem''}
While classical utility- or regret-based frameworks offer a structure for weighing these risks, they are not designed to handle uncertainties that are \emph{deep} in the sense that stakeholders may not agree upon their probabilities \citep{lempert_complex:2002} or \emph{irreducible} in the sense that there is not an objective truth that better models and data can identify \citep{DossGollin:2019}.\footnote{Unless we believe everything is pre-determined, in which case why bother with climate adaptation\ldots}
Examples of such uncertainties include how much greenhouse gasses humans will emit in the future or whether the U.S. federal government will continue to subsidize flood insurance for homeowners\james{Add some references -- Klaus suggests \citet{savage:1954} or similar}.
In response, a wide range of fields have developed scenario-based methods\ldots.
This leads to the ``Multiple PDF Problem'' \citep{sharma_rcp:2021}\ldots.
A key question, then, facing the designers, builders, regulators, owners, and users of built facilities is \emph{to which scenario should infrastructure be designed?}

\paragraph{Set up house elevation as an example}
One example is building codes and guidelines\ldots.
Prior studies have found that floodproofing and building-scale vulnerability reduction measures, including house elevation, can effectively reduce local flood damages in many contexts \citep{demoel_reducing:2014,deruig_building:2020,kreibich_building:2005,slotter_floodproofing:2020,Rozer:2016dn,mobley_mitigation:2020,aerts_cost:2018}.
Official guidance for homeowners, notably from \gls{fema}, recommends elevating to the \gls{bfe} (typically the \SI{100}{year} flood) plus a freeboard \citep{fema_retrofitting:2014,asce_24-14:2015,fema_retrofitting:2014} but recent suggests scope for improvement.
For example, \citet{xian_elevation:2017} used a cost-benefit analysis to demonstrate that tailoring recommendations to the inital elevation of a structure can reduce expected costs.
\citet{zarekarizi_suboptimal:2020} show that neglecting uncertainty in discount rate, house lifespan, flood risk, and depth-damage curves can lead to maladaptation.
Yet these studies are silent on the question of how nonstationary flood hazard should factor into this decision.

\paragraph{Nonstationarity motivates the case study}
Nonstationarity is particularly relevant in coastal communities where \gls{rslr} is expected to drive future flood risk.
As a didactic case study, we consider the problem of how high a homeowner should elevate their structure to mitigate future flood losses, illustrated in \cref{fig:house-sketch},\james{Need to revisit this picture} given stochastic flood peaks and deeply uncertain \gls{rslr}.
\Gls{rslr} is driven mainly by physical processes like (\ldots, West Antarctic Ice Sheet, \ldots\klaus{You wrote something here that I can't read -- I see something that looks like ICM. I assume Tony and Kelsey papers are relevant as well?}) \citep{kopp_probabilistic:2014,kopp_evolving:2017}.
Two key uncertainties identified by previous studies are
\begin{enumerate*}[label=(\roman*)]
    \item which emissions pathway (\eg, \gls{rcp} scenario) will we experience and
    \item how will polar ice sheets respond to warming \citep{wong_brick0.2:2017,ruckert_coastal:2019,wong_nola:2017,deconto_antarctica:2016}.
\end{enumerate*}
Simulations of \gls{rslr} are available to decision makers grouped by \gls{rcp} scenario and model structure.
For a given combination of \gls{rcp} scenario and model, results are typically presented and interpreted as probabilistic, but this is not the same as giving decision-makers a single \gls{pdf}.
This is the ``Multiple \gls{pdf} Problem'' described in, \eg, \citet{sharma_rcp:2021}.
Thus, \emph{which scenario/\gls{pdf} should we design for?}

@@

\begin{figure}
    \centering
    \includegraphics[height=2in]{uconn-elevateA}
    \caption{
        Conceptual sketch illustrating the path from historical data to FEMA's guidance.
        This figure \emph{needs to be revised} (KATERINA?) to have three panels, of which this is the third.
        (a): A time series of historical floods.
        (b): A \gls{pdf} of the flood peak.
        (c): as shown, but with waves eliminated.
        This sketch figure is from \citet{patten_elevate:2016}.
    }\label{fig:house-sketch}
\end{figure}

@@

In this section we present a general framework for decision making under deep uncertainty.
We begin with terms and definitions that are broadly consistent with common adaptive frameworks\james{add refs}\klaus{did I read this right?}.
In \cref{sec:methods-weight} we present a Bayesian model for weighting \glspl{sow}.
In \cref{sec:methods-iterative} we discuss how this framework can be integrated into frameworks for iterative engagement with experts and stakeholders to expand and frame the model.

@@

We start by modeling the performance of a decision $x \in \mathcal{X}$.
Outcomes depend both on the decision and on a state of the world $s \in \Omega$ that describes all relevant uncertainties.
To model outcomes $u \in \mathcal{U}$, we use a system model $f: \mathcal{X}, \Omega \rightarrow \mathcal{U}$ \citep[we generally follow the notation of][]{mcphail_robustness:2019} which we assume to be deterministic.
If $f$ is a stochastic function, we can define its metrics in terms of expectations, \eg $u_{ij} = \mathbb{E}\qty[u | x=x_i, s=s_j]$, which can be approximated through techniques like Monte Carlo sampling.

@@

\citet{mcphail_robustness:2019} split the problem of aggregating \gls{sow} metrics into decision metrics into two steps: ``subsetting'' (\eg, single value, all values, subset of values) and ``metric calculation'' (\eg, mean, variance, skew, kurtosis).\klaus{You say something about see discussion in \citet{mcinerney_robust:2012} -- please elaborate}
We generalize this to
\begin{equation}
    m_i = g(\qty{u_{i1}, u_{i2}, \ldots, u_{iJ}}, \qty{w_1, w_2, \ldots, w_J}),
\end{equation}
where $g$ is an \emph{aggregating function} describing the ``metric calculation'' step and the $w_j$ describe weights given to each \gls{sow}.
A optional, but likely useful, interpretation of the weighted samples $\qty{w_j, u_{ij} \forall j=1, \ldots, J}$ is an empirical \gls{pdf}, in which case $g$ maps a \gls{pdf} of future outcomes to the metrics $m_i$.\footnote{perhaps this belongs in the Discussion}
This is a flexible framework; \cref{tab:literature-weighting} shows some methods for robust decision making from the literature using our notation.\james{Add some references to the table}

@@

\paragraph{To think  about}
I have two flavors of this idea presented here!
\Cref{fig:framework}\james{Updates for \cref{fig:framework}: Don't need to say here that $f$ is deterministic. Larger text and darker color for questions. Rename $p(s)$ as ``prior over parameters and model structures''} takes a more Bayesian focus: the goal is to reason about properties of the \emph{distribution} over outcomes $p(u | x=x_i)$.
The text follows \citet{mcphail_robustness:2019} more.
I'm not sure which is easier to understand.

@@

If the common practice of weighting all scenarios equally is applied ($w_j \propto 1$ in \cref{tab:literature-weighting}), a tension emerges: we want to \emph{explore} highly unlikely but theoretically possible trajectories to understand their consequences, but we don't want extremely unlikely scenarios to dominate our decision.

Some aims:
\begin{enumerate}
    \item Assumptions should be as transparent and visible as possible to facilitate critique and dialogue\klaus{I moved this up}
    \item We should be invariant to the parameterization of $s$ -- if we sample population uniformly from 1 million to 10 million or $\log_{10}$ population uniformly from \num6 to 7, we should get the same answer
    \item We should be invariant to the sampling of $s$:
          \begin{enumerate}
              \item if we include scientifically interesting but extremely low-probability scenarios (\eg, if someone created \gls{rcp} 45), our esimtates of $m_i$ should not change meaningfully.\james{Explain why}
              \item if we include nearly redundant scenarios (\eg, if we are studying \gls{rcp} 2.6, 4.5, 6.0, and 8.5 and we then add results from a \gls{rcp} 6.01 experiment), our estimates of $m_i$ should not change meaningfully.\james{Explain why}
          \end{enumerate}
\end{enumerate}
We can do this with probability if we have a target distribution $p(s)$.
We return to the question of how to choose this in \cref{sec:methods-prior}.

@@

\begin{figure}
    \centering
    \includegraphics[height=2.5in, width=0.6\textwidth, keepaspectratio=true]{xlrm}
    \caption{
        Diagram showing uncertainties ($X$; red), levers ($L$; yellow), system relationships ($R$; gray), and metrics ($M$; blue).
    }\label{fig:xlrm}
\end{figure}

@@

Coastal floods are often decomposed into changes in local sea level \citep{kopp_evolving:2017,kopp_probabilistic:2014,wong_brick0.2:2017} plus storm surge \citep{garner_slrise:2018,cagigal_emulator:2020,rueda_surge:2016}.
We neglect waves and hydrodynamics for simplicity.

\gls{rslr}:
\begin{enumerate}
    \item We have 2 models of ice sheet dynamics (3? Vivek and Tony are trying to tell me what models the data from \citet{ruckert_coastal:2019} actually comes from)
    \item We have 4 \gls{rcp} scenario
    \item We use the BRICK model \citep{wong_brick0.2:2017} simulations from \citet{ruckert_coastal:2019} to define $J$ \glspl{sow}.
\end{enumerate}
Storm surge:
\begin{enumerate}
    \item We have a $N$ year observational record
    \item We separate out storm surge from the background trend in some standard way
    \item We model storm surge as a stationary GEV model
    \item We place a prior on the return level (data space) rather than a prior on the parameters themselves (except the shape parameter -- we put a restrictive prior for it to be positive)\james{arguably we should stick to boring priors here -- the question being whether it's better to say we use iterative checks to improve the priors, or whether we want to keep things simple}
    \item We draw $K$ sets of parameters $\qty(\mu_k, \sigma_k, \xi_k)$
\end{enumerate}
Thus a \gls{sow} is defined just an 81 year time series of \gls{lsl}.
We will see what we do with the $K$ draws of storm surge parameters shortly.
\begin{figure}
    \caption{
        INSERT HERE: figure showing time series of observed surge and \gls{lsl} with notable storms indicated, as well as projections of future \gls{lsl} under all eight models (two BRICK, four \gls{rcp})
    }
\end{figure}

@@

\subsection{A simplified didactic system model}

@@

\paragraph{Prior on outputs only}
Following \citet{garner_slrise:2018}, \citet{oddo_coastal:2017}, and \citet{lempert_slr:2012} we place a prior on \gls{rslr} in 2100.\klaus{You suggest looking at another paper. Are you referring to this?\\\fullcite{sriver_sealevel:2018}}

@@

                    More recent discussions of Bayesian philosophy \citep{jaynes_probability:2003,McElreath:2016vu,Gelman:2014tc,bernardo_bayesian:1994} also emphasize a philosophical view of probability as a language with which to reason about the unknown rather than a statement of objective truth \citep[see][for a thorough discussion of Bayesian philosophy]{gelman_philosophy:2013}.\klaus{Am I reading right that you say ``maybve have this in intro to motivate the analysis?''}

@@

              \item A goal is to make -- intrinsically flawed and subjective -- modeling choices as transparent as possible. Since we can't be right, we should make it as easy as possible for others to understand and critique our assumptions\james{Focus on this!}

@@

\begin{enumerate}
    \item MARISA\james{details}
    \item PSIRC\james{details}
    \item Rice University (for startup)
    \item Tor Erlend Fjelde for helpful advice on implementing the GEV prior using \texttt{Turing.jl}.
    \item For many journals, a code and data statement will go here.
\end{enumerate}
